### 2013-03-24 mcmc.tex
tweaks and line breaking

Given this pdf $p(x)$, we can define \emph{expectation values} $E[x]$
for $x$ or for any quantity that can be expressed as a function $q(x)$
of $x$:
\begin{eqnarray}
E[x] &\equiv& \int x\,p(x)\,\dd x
\\
E[q] &\equiv& \int q(x)\,p(x)\,\dd x
\quad ,
\end{eqnarray}
where the integrals are implicitly definite integrals over the domain
of $x$ (all the parts of $x$ space in which $p(x)$ is finite) and the
integrals are multi-dimensional if $x$ is multi-dimensional.  These
expectation values are the mean values of $x$ and $q(x)$ under the
pdf.  A good sampling---really the definition of a good
sampling---makes the sampling approximation to these integrals
accurate.  With a good sampling $\setof{x_k}_{k=1}^K$ the integrals
get replaced with sums over samples $x_k$:
\begin{eqnarray}
E[x] &\approx& \frac{1}{K}\,\sum_{k=1}^K x_k
\\
E[q] &\approx& \frac{1}{K}\,\sum_{k=1}^K q(x_k)
\quad .
\end{eqnarray}
That is, a sampling is good when any expectation value of interest is
accurately computed via the sampling approximation.  The word
``accurately'' here translates into some kinds of theorems about
limiting behavior; the general idea is that the sampling approximation
becomes exact as $K$ goes to infinity.  The size $K$ of the sampling
you need \emph{in practice} will depend on the expectations you want
to compute, and the accuracies you need.

>>>>

Given this pdf $p(x)$, we can define \emph{expectation values} $E[x]$
for $x$ or for any quantity that can be expressed as a function $q(x)$
of $x$:
\begin{eqnarray}
E[x] &\equiv& \int x\,p(x)\,\dd x
\\
E[q] &\equiv& \int q(x)\,p(x)\,\dd x
\quad ,
\end{eqnarray}
where again the integrals are implicitly definite integrals over the
entire domain
of $x$ (all the parts of $x$ space in which $p(x)$ is finite) and the
integrals are multi-dimensional if $x$ is multi-dimensional.
These expectation values are the mean values of $x$ and $q(x)$ under
the pdf.  A good sampling---really the definition of a good
sampling---makes the sampling approximation to these integrals
accurate.
With a good sampling $\setof{x_k}_{k=1}^K$ the integrals get replaced
with sums over samples $x_k$:
\begin{eqnarray}
E[x] &\approx& \frac{1}{K}\,\sum_{k=1}^K x_k
\\
E[q] &\approx& \frac{1}{K}\,\sum_{k=1}^K q(x_k)
\quad .
\end{eqnarray}
That is, a sampling is good when any expectation value of interest is
accurately computed via the sampling approximation.
The word ``accurately'' here translates into some kinds of theorems
about limiting behavior; the general idea is that the sampling
approximation becomes exact as $K$ goes to infinity.
The size $K$ of the sampling you need \emph{in practice} will depend
on the expectations you want to compute, and the accuracies you need.
